---
title: "Influencing Reign FC social media consumption and brand attitude"
author: Andrew Nalundasan
date: August 28, 2021
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo = FALSE}
# Course: OMSBA 5210
# Purpose: DTC - Slides
# Date: August 27, 2021
# Author: Andrew Nalundasan
```

```{r echo = FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 

# NOTE, DO NOT CLEAR PACKAGES, IF YOU DO IT WILL NOT RUN
```


```{r message=FALSE, include=FALSE}

library(ggannotate)    # annotation tool
library(scales)        # to get $ and , on axis in graph
library(tidyverse)     # contains ggplot2, dplyr, and several other packages
library(vtable)        # NHK special
library(gghighlight)   # visual formatting - highlights
library(ggiraph)       # ggiraph
```


```{r include=FALSE}
# read data into environment and assign to object
soccer <- read_csv("../02_raw_data/Seattle_Reign.csv")

# make updates to data here so can pull from cleaned data
soccer_updates <- soccer %>% 
  # transform Interest responses to numeric
  mutate(Interest = str_replace_all(Interest, "I have a small amount of interest", "1")) %>% 
  mutate(Interest = str_replace_all(Interest, "I consider myself to be a low-level fan of this team", "2")) %>% 
  mutate(Interest = str_replace_all(Interest, "I consider myself to be a moderate fan of this team", "3")) %>% 
  mutate(Interest = str_replace_all(Interest, "I consider myself to be a loyal fan of this team", "4")) %>% 
  mutate(Interest = str_replace_all(Interest, "I live and die with this team", "5")) %>% 
  # make Interest a factor
  mutate(Interest = as.factor(Interest)) %>% 
  # media variables
  mutate(Media1 = str_sub(Media1, -2)) %>% 
  mutate(Media3 = str_sub(Media3, -2)) %>%
  mutate(Media4 = str_sub(Media4, -2)) %>%
  mutate(Media5 = str_sub(Media5, -2)) %>%
  mutate(Media6 = str_sub(Media6, -2)) %>%
  mutate(Media12 = str_sub(Media12, -2)) %>%
  mutate(Media7a = str_sub(Media7a, -2)) %>%
  mutate(Media7b = str_sub(Media7b, -2)) %>% 
  # sponsor variables
  mutate(across(starts_with('Spnbuy'), function(x) str_sub(x, -1))) %>% 
  mutate(across(starts_with('Spnbuy'), function(x) as.numeric(x))) %>% 
  # grab last 2 characters of string and change class to numeric
  mutate(Travel1 = str_sub(Travel1, -2)) %>%  
  mutate(Travel1 = as.numeric(Travel1)) %>% 
  mutate(Travel2 = str_sub(Travel2, -2)) %>%
  mutate(Travel2 = as.numeric(Travel2)) %>% 
  mutate(Travel3 = str_sub(Travel3, -2)) %>% 
  mutate(Travel3 = as.numeric(Travel3)) %>% 
  mutate(Seat1 = str_to_title(Seat1)) %>% 
  # grab last 2 characters of Promo variables
  mutate(across(starts_with('Promo'), function(x) str_sub(x, -2))) %>% 
  mutate(across(starts_with('Promo'), function(x) as.numeric(x)))
  
# change all character responses to numeric scale to analyze as likert scale
soccer_updates[soccer_updates == "Strongly disagree"] <- "-3"
soccer_updates[soccer_updates == "Strongly Disagree"] <- "-3"
soccer_updates[soccer_updates == "Disagree"] <- "-2"
soccer_updates[soccer_updates == "Somewhat disagree"] <- "-1" 
soccer_updates[soccer_updates == "Somewhat Disagree"] <- "-1" 
soccer_updates[soccer_updates == "Neutral"] <- "0" 
soccer_updates[soccer_updates == "Somewhat agree"] <- "1"
soccer_updates[soccer_updates == "Somewhat Agree"] <- "1"
soccer_updates[soccer_updates == "Agree"] <- "2" 
soccer_updates[soccer_updates == "Strongly agree"] <- "3"
soccer_updates[soccer_updates == "Strongly Agree"] <- "3"
soccer_updates[soccer_updates == "Very Unimportant"] <- "1"
soccer_updates[soccer_updates == "Very Important"] <- "7"
soccer_updates[soccer_updates == "Prefer not to answer"] <- "Undisclosed"
soccer_updates[soccer_updates == "Very Dissatisfied"] <- "1"
soccer_updates[soccer_updates == "Very Satisfied"] <- "7"
soccer_updates[soccer_updates == "Single"] <- "1"
soccer_updates[soccer_updates == "Married/Partnered"] <- "2"
soccer_updates[soccer_updates == "Some High School"] <- "1"
soccer_updates[soccer_updates == "High School Graduate"] <- "2"
soccer_updates[soccer_updates == "Some College"] <- "3"
soccer_updates[soccer_updates == "College Graduate"] <- "4"
soccer_updates[soccer_updates == "Graduate Degree"] <- "5"
soccer_updates[soccer_updates == "Other"] <- "6"
```

```{r eval=FALSE, include=FALSE}

# Full screen intro of MY FACE

# Hello everyone. Thank you for this opportunity to present to you today. My name is Andrew Nalundasan, and I will be covering the findings from my recent analysis regarding potential methods of increasing brand attitude and enhancing gameday experience for the Reing FC. In this video, I will give a brief overview of the data set and the analyses performed, I will speak about the findings and recommendations that came out of the analyses, and I'll wrap it up with our key takeaways. 

# Start sharing screen and begin presentation
```


Introduction
===============================================

+ The Data:

    + Survey distributed online via email list provided by Seattle Reign FC 
    + 684 respondents
    + Data has been anonymized - no privacy concerns for Reign FC fans

+ Insights into respondent behaviors and levels of satisfaction

    + People are proud to be associated with the Reign
    + Especially true when the team are good role models to children
    + Facebook is the preferred choice of social media when accessing Reign FC information
        

Fans use Facebook to keep up with the Reign FC
===============================================

<div style="float: left; width: 35%;">

+ Fans prefer using Facebook to get Reign FC information

+ Website is being used

+ Reign FC presence on Twitter can be improved

+ Increasing social media activity should be made a priority

</div>

<div style="float: left; width: 65%;">

```{r echo=FALSE, message=FALSE, warning=FALSE}
# media intentions
# select variables that will answer research question 1
q1 <- soccer_updates %>% 
  select(Cost3, Clink1, Starfir1, Attend17, Seat1, Ticket1, Expsat1,
         Media8_1:Media8_5, Media9, Media10, Media1:Media6, Media12, Media7a, Media7b,
         Buymer1, Buyonl1, BuyMat1, BuyStor1, BuySpon1, Merimp20, Merimp22, Merimp24, 
         Gender:Age, 
         Interest, Gamewit1:Gamewit4)

media_int <- q1 %>% 
  # select variables to answer the question
  select(Media8_1:Media7b, Gender:Age, Interest) %>% 
  # rename relevant variables
  rename(Website = Media8_1, Facebook = Media8_2, Twitter = Media8_3, Instagram = Media8_4, YouTube = Media8_5) %>%
  # change remaining "Media" variables to numeric
  mutate(across(starts_with("Media"), function(x) as.numeric(x)))

# finding 1 visual

q1_palette <- c("#999999", "#66CCFF", "#3399FF")

q1_vis_wrangle <- media_int %>% 
  select(Website:YouTube, Interest) %>% 
  pivot_longer(cols = -c(Interest)) %>% 
  group_by(name, Interest) %>% 
  summarise(value = sum(value, na.rm = TRUE)) %>% 
  group_by(Interest) %>% 
  arrange(-value) %>% 
  slice(2)
  
q1_vis <- q1_vis_wrangle %>% 
  mutate(Interest = as.factor(Interest),
         name = as.factor(name)) %>% 
  ggplot(mapping = aes(x = Interest, y = value, fill = name)) + 
  geom_col(position = "dodge") +
  scale_fill_manual(values = q1_palette) +
  coord_flip() + 
  theme_classic() + 
  theme(axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position = "none") +
  labs(y = "Number of people accessing media", 
       x = "Media Popularity",
       title = "Top media outlets for Reign FC", 
       subtitle = "Enhanced social media strategies will increase team pride") + 
  
  geom_text(data = data.frame(x = 4.99646068843984, y = 209.149655187183, label = "Facebook"),
            mapping = aes(x = x, y = y, label = label),
            colour = "#3399FF", fontface = 2, inherit.aes = FALSE) +
  
  geom_text(data = data.frame(x = 4.63799768489595, y = 585.234940631178, label = "Facebook"),
            mapping = aes(x = x, y = y, label = label),
            colour = "#3399FF", fontface = 2, inherit.aes = FALSE) +

  
  geom_text(data = data.frame(x = 2.01470024987025, y = 53.3602812815799, label = "Twitter"),
            mapping = aes(x = x, y = y, label = label),
            colour = "#66CCFF", fontface = 2, inherit.aes = FALSE) + 
  
  geom_text(data = data.frame(x = 3.04120794183683, y = 226.189117958109, label = "Website"),
            mapping = aes(x = x, y = y, label = label),
            colour = "#999999", fontface = 2, inherit.aes = FALSE) +
  
  geom_text(data = data.frame(x = 0.98, y = 54.5773857652174, label = "Website"),
            mapping = aes(x = x, y = y, label = label),
            colour = "#999999", fontface = 2, inherit.aes = FALSE)

q1_vis
# ggannotate(q1_vis)

# save to use in memo
# ggsave(filename = "q1_vis.png", plot = q1_vis)

```


</div>

Team of good role models helps drive brand attitude
===============================================

<div style="float: left; width: 35%;">

+ Brand attitude was found to be highly correlated with sentiments about the Reign being good role models to children

+ Reign FC should have policy for team members to avoid the negative spotlight 

+ Fan support from parents will drive support from children

    - Children are likely to be more active on social media

+ Cultivating a strong fanbase in today's children will lead to strong fanbase in the future

</div>

<div style="float: left; width: 65%;">

```{r echo=FALSE, message=FALSE, warning=FALSE}
# visual telling story about brand attitude

# wrangle data
q3 <- soccer_updates %>% 
  select(Interest, BIRG1, RoleMod2, Posaff1, Negaff1, 
         Gender:Age)

q3[, c(1:5)] <- sapply(q3[, c(1:5)], as.numeric)

brand_att <- q3 %>% 
  filter(str_detect(Gender, "ale"))

# build the viz
cb_palette <- c("#cccccc", "#00aedb")

q3_vis <- brand_att %>% 
  group_by(BIRG1, RoleMod2) %>% 
  summarize(count = n()) %>% 

  ggplot(aes(BIRG1, RoleMod2)) + 
  geom_tile_interactive(aes(fill = -count)) +  
  scale_fill_distiller(palette = "RdPu") +
  
  #scale_x_continuous(breaks = c("Strongly Disagree", "Neutral", "Strongly Agree")) +
  coord_flip() +
  theme_classic() + 
  theme(axis.line.x = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") + 
  labs(x = "", 
       y = "",
       title = "Major support from people that believe Reign are role models",
       subtitle = "Reign can have a positive impact to children and the community") + 
  
  # annotations
  geom_text(data = data.frame(x = 3.45013154997636, y = -3.50221388195219, label = "Most Pride"),
            mapping = aes(x = x, y = y, label = label),
            hjust = 0L, colour = "#990066", fontface = 2, inherit.aes = FALSE) + 
  
  geom_text(data = data.frame(x = -2.06558111093393, y = -3.50221388195219, label = "Least Pride"),
            mapping = aes(x = x, y = y, label = label),
            hjust = 0L, colour = "#FFCCCC", fontface = 2, inherit.aes = FALSE) +
  
  geom_text(data = data.frame(x = -3.80993805601707, y = -3.09115165591085, label = "Bad Role Model"),
            mapping = aes(x = x, y = y, label = label),
            hjust = 0.4, colour = "#FFCCCC", fontface = 2, inherit.aes = FALSE) + 

  geom_text(data = data.frame(x = -3.70922298458263, y = 2.94268974345045, label = "Great Role Model"),
            mapping = aes(x = x, y = y, label = label),
            colour = "#990066", fontface = 2, inherit.aes = FALSE)

ggiraph(ggobj = q3_vis)

```

</div>


Key Takeaways
===============================================

+ Robust data set of 684 survey respondents

+ Enhancing social media strategy could help garner interest in the team

+ Future study analyzing social media trends to verify increased interest in the team

+ The Reign players being good role models for kids is a strong driver in brand attitude

+ Future study on merch sold in children's sizes to verify brand attitude

+ Support from parents will drive support from children, who are the ones that utilize social media outlets



Thank You
===============================================
