---
title: "Data Translation Challenge"
author: "Andrew Nalundasan"
date: "August 27, 2021"   
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE}
# Course: OMSBA 5210, Seattle University
# Purpose: DTC Technical Appendix
# Date: August 27th, 2021
# Author: Andrew Nalundasan

```

# Load Libraries

```{r message=FALSE, include=FALSE}
library(tidyverse)     # contains ggplot2, dplyr, and several other packages
library(ggannotate)    # annotation tool
library(gridExtra)     # use to put graphs together in the same frame
library(janitor)       # contains tidyverse functions for cross-tables
library(knitr)         # contains some table formatting functions
library(GGally)        # contains a custom correlation plot
library(scales)        # to get $ and , on axis in graph
library(corrplot)      # used for correlation plot with good looks below
library(tidyr)         # tidy r
library(kableExtra)    # extra kable formatting
library(vtable)        # NHK special
library(gghighlight)   # visual formatting - highlights
library(agricolae)     # for statistical testing
library(huxtable)      # table formatting
library(jtools)        # export summs table
library(car)           # linear hypothesis

```



# Load and Transform Data

1. Make updates to data

2. Wrangle 6 subsets of data to answer the 6 different research questions

    1. Determine the primary factors that impact attendance intentions, media consumption intentions, and merchandise consumption intention. 
    2. Determine the factors that impact satisfaction (Performance, Outcome, Matchday Satisfaction).
    3. Determine ways to increase brand attitude.
    4. Investigate purchasing habits of corporate partner products. 
    5. Investigate ways to improve gameday experience. 
    6. Identify viable market segments

```{r include=FALSE}
# read data into environment and assign to object
soccer <- read_csv("../02_raw_data/Seattle_Reign.csv")

# make updates to data here so can pull from cleaned data
soccer_updates <- soccer %>% 
  # transform Interest responses to numeric
  mutate(Interest = str_replace_all(Interest, "I have a small amount of interest", "1")) %>% 
  mutate(Interest = str_replace_all(Interest, "I consider myself to be a low-level fan of this team", "2")) %>% 
  mutate(Interest = str_replace_all(Interest, "I consider myself to be a moderate fan of this team", "3")) %>% 
  mutate(Interest = str_replace_all(Interest, "I consider myself to be a loyal fan of this team", "4")) %>% 
  mutate(Interest = str_replace_all(Interest, "I live and die with this team", "5")) %>% 
  # make Interest a factor
  mutate(Interest = as.factor(Interest)) %>% 
  # media variables
  mutate(Media1 = str_sub(Media1, -2)) %>% 
  mutate(Media3 = str_sub(Media3, -2)) %>%
  mutate(Media4 = str_sub(Media4, -2)) %>%
  mutate(Media5 = str_sub(Media5, -2)) %>%
  mutate(Media6 = str_sub(Media6, -2)) %>%
  mutate(Media12 = str_sub(Media12, -2)) %>%
  mutate(Media7a = str_sub(Media7a, -2)) %>%
  mutate(Media7b = str_sub(Media7b, -2)) %>% 
  # sponsor variables
  mutate(across(starts_with('Spnbuy'), function(x) str_sub(x, -1))) %>% 
  mutate(across(starts_with('Spnbuy'), function(x) as.numeric(x))) %>% 
  # grab last 2 characters of string and change class to numeric
  mutate(Travel1 = str_sub(Travel1, -2)) %>%  
  mutate(Travel1 = as.numeric(Travel1)) %>% 
  mutate(Travel2 = str_sub(Travel2, -2)) %>%
  mutate(Travel2 = as.numeric(Travel2)) %>% 
  mutate(Travel3 = str_sub(Travel3, -2)) %>% 
  mutate(Travel3 = as.numeric(Travel3)) %>% 
  mutate(Seat1 = str_to_title(Seat1)) %>% 
  # grab last 2 characters of Promo variables
  mutate(across(starts_with('Promo'), function(x) str_sub(x, -2))) %>% 
  mutate(across(starts_with('Promo'), function(x) as.numeric(x)))
  
# change all character responses to numeric scale to analyze as likert scale
soccer_updates[soccer_updates == "Strongly disagree"] <- "-3"
soccer_updates[soccer_updates == "Strongly Disagree"] <- "-3"
soccer_updates[soccer_updates == "Disagree"] <- "-2"
soccer_updates[soccer_updates == "Somewhat disagree"] <- "-1" 
soccer_updates[soccer_updates == "Somewhat Disagree"] <- "-1" 
soccer_updates[soccer_updates == "Neutral"] <- "0" 
soccer_updates[soccer_updates == "Somewhat agree"] <- "1"
soccer_updates[soccer_updates == "Somewhat Agree"] <- "1"
soccer_updates[soccer_updates == "Agree"] <- "2" 
soccer_updates[soccer_updates == "Strongly agree"] <- "3"
soccer_updates[soccer_updates == "Strongly Agree"] <- "3"
soccer_updates[soccer_updates == "Very Unimportant"] <- "1"
soccer_updates[soccer_updates == "Very Important"] <- "7"
soccer_updates[soccer_updates == "Prefer not to answer"] <- "Undisclosed"
soccer_updates[soccer_updates == "Very Dissatisfied"] <- "1"
soccer_updates[soccer_updates == "Very Satisfied"] <- "7"
soccer_updates[soccer_updates == "Single"] <- "1"
soccer_updates[soccer_updates == "Married/Partnered"] <- "2"
soccer_updates[soccer_updates == "Some High School"] <- "1"
soccer_updates[soccer_updates == "High School Graduate"] <- "2"
soccer_updates[soccer_updates == "Some College"] <- "3"
soccer_updates[soccer_updates == "College Graduate"] <- "4"
soccer_updates[soccer_updates == "Graduate Degree"] <- "5"
soccer_updates[soccer_updates == "Other"] <- "6"

```

# Research Question 1: Determine the primary factors that impact attendance intentions, media consumption intentions, and merchandise consumption intention. 

+ wrangle data subset to answer question 1

```{r}
# Question 1 - Determine the primary factors that impact attendance intentions, media consumption intentions, and merchandise consumption intention. 

# select variables that will answer research question 1
q1 <- soccer_updates %>% 
  select(Cost3, Clink1, Starfir1, Attend17, Seat1, Ticket1, Expsat1,
         Media8_1:Media8_5, Media9, Media10, Media1:Media6, Media12, Media7a, Media7b,
         Buymer1, Buyonl1, BuyMat1, BuyStor1, BuySpon1, Merimp20, Merimp22, Merimp24, 
         Gender:Age)

```

```{r}
# select and mutate variables that answer Attendance Intentions
attendance_int <- q1 %>% 
  select(c(1:7, Gender:Age))

# change responses to numeric
attendance_int[, c(1:7)] <- sapply(attendance_int[, c(1:7)], as.numeric)
```


```{r}
# select and update variables that answer Media Consumption Intentions
media_int <- q1 %>% 
  # select variables to answer the question
  select(Media8_1:Media7b, Gender:Age) %>% 
  # rename relevant variables
  rename(Website = Media8_1, Facebook = Media8_2, Twitter = Media8_3, Instagram = Media8_4, YouTube = Media8_5) %>%
  # change remaining "Media" variables to numeric
  mutate(across(starts_with("Media"), function(x) as.numeric(x)))
  
# grouped dataset
media_int_grouped <- media_int %>% 
  pivot_longer(cols = -c(Gender:Age)) %>% 
  group_by(name) %>% 
  summarise(value = mean(value, na.rm = TRUE))
```

```{r}
# select and mutate variables that answer Merchandise Consumption Intentions
merch_int <- q1 %>% 
  select(Buymer1:Merimp24, Gender:Age)

# change responses to numeric
merch_int[, c(1:8)] <- sapply(merch_int[, c(1:8)], as.numeric)
```


## Base EDA Step 1: Uni-variate non-graphical EDA

```{r}
# top of the dataset and look each subset
head(attendance_int)
vtable(attendance_int)

head(media_int)
vtable(media_int)

head(merch_int)
vtable(merch_int)

```

+ data appears to be tidy

    - data in each column is of the same variable type
    - no duplicate columns
    - each row is an individual's response to Reign survey
    - survey responses all uniform formatting (changed to cardinal responses and set as.numeric)
    - numeric variables and categorical
    
```{r}
# check descriptive statistics of media intentions
summary(media_int)
```

**Comments**

    - most variables seem to be right skewed since mean >> median
        - scale for most variables is -3 -> 3, so makes sense that 0 is median for many
        - right skewedness means more positive responses to survey questions
    - lots of NA's that will need to be filtered out
    
**Questions**

+ how can I gauge media intentions with these variables?

+ which variables drive media intentions?

+ which form of media is most/least popular?

    - Figure out which forms of media are most popular and assume intentions in those media forms will continue
    - Most popular media outlets will be where Reign can focus ads and promos
    
```{r}
# check descriptive statistics of merch intentions
summary(merch_int)
```

**Comments**

    - converted variables with agree/disagree character responses to numeric cardinal scale

**Questions**

+ what are the demographics of who wants to buy merch or not?

```{r}
# check descriptive statistics for attendance intentions
summary(attendance_int)
```

**Comments**

    - all variables on the scale of -3 -> 3
    - accounting for ticket cost, thoughts about Century Link vs. Starfire venue, likelihood of attendance, seating setup, buying tickets online

**Questions**

+ what are the demographics of who wants to attend matches or not?

## Base EDA Step 2: Uni-variate graphical EDA

- Examine each variable individually
- Examine how many observations in each variable

```{r}
# SOCIAL media intentions - how many times accessed per week
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Website
ggplot(data = media_int, mapping = aes(x = Website)) +
  geom_bar(),

# Facebook
ggplot(data = media_int, mapping = aes(x = Facebook)) +
  geom_bar(), 

# Twitter
ggplot(data = media_int, mapping = aes(x = Twitter)) +
  geom_bar(),

# Instagram
ggplot(data = media_int, mapping = aes(x = Instagram)) + 
  geom_bar(),

# YouTube
ggplot(data = media_int, mapping = aes(x = YouTube)) + 
  geom_bar(),

ncol = 2 )
```

**Comments**

    - appears that the Website gets 1 hit per week is the strongest social media outlet
    - IG appears to be the weakest social media outlet
    - YouTube has some popularity
    - Twitter has spikes of interest
    - Website and FB are similar from 2+
    - Most media consumption happens on Website
    - YouTube is second most consumed media
    
+ Other social media is weak. Propose to beef up strategies around Facebook, Instagram, and Twitter
    
**Questions**

+ why is the Website getting the most hits?

+ why does YouTube getting more hits than other social media outlets?

    - Does the Reign broadcast their games on YouTube?

```{r}
# non-social media intentions
grid.arrange(

# Media9
ggplot(data = media_int, mapping = aes(x = Media9)) +
  geom_bar(),

# Media10
ggplot(data = media_int, mapping = aes(x = Media10)) +
  geom_bar(), 

# Media1
ggplot(data = media_int, mapping = aes(x = Media1)) +
  geom_bar(),

# Media3
ggplot(data = media_int, mapping = aes(x = Media3)) + 
  geom_bar(),

# Media4
ggplot(data = media_int, mapping = aes(x = Media4)) + 
  geom_bar(),

# Media5
ggplot(data = media_int, mapping = aes(x = Media5)) +
  geom_bar(), 

# Media6
ggplot(data = media_int, mapping = aes(x = Media6)) +
  geom_bar(),

# Media12
ggplot(data = media_int, mapping = aes(x = Media12)) + 
  geom_bar(),

# Media7a
ggplot(data = media_int, mapping = aes(x = Media7a)) + 
  geom_bar(),

# Media7b
ggplot(data = media_int, mapping = aes(x = Media7b)) + 
  geom_bar(),

ncol = 2 )
```

**Comments**

    - More positive reactions than negative
    - Media4 and Media5 have most negative feelings
        - Media4: Radio ads
        - Media5: Media publicity
    - Media12 the most positively received media
        - Media12: EMAILS
        - Really??
    - Media9: Newspaper / digital sports page

**Questions**

+ Why are EMAILS the most positively received form of media?

    - Perhaps because promo codes are included in emails to get ticket discounts/special offers
    - Perhaps this is why the website is the most popular social media outlet too

```{r}
# merch intentions - 
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Buymer1
ggplot(data = merch_int, mapping = aes(x = Buymer1)) +
  geom_bar(),

# Buyonl1
ggplot(data = merch_int, mapping = aes(x = Buyonl1)) +
  geom_bar(), 

# BuyMat1
ggplot(data = merch_int, mapping = aes(x = BuyMat1)) +
  geom_bar(),

# BuyStor1
ggplot(data = merch_int, mapping = aes(x = BuyStor1)) + 
  geom_bar(),

# BuySpon1
ggplot(data = merch_int, mapping = aes(x = BuySpon1)) + 
  geom_bar(),

ncol = 2 )
```

**Comments**

    - mostly positive sentiments on these questions
    - lots of people intending to buy merch in the future (Buymer1)
    - Buying merch online skewed slightly positively (Buyonl1)
        - online store doesn't seem to be enticing
    - Intentions to buy merch at match (BuyMat1)
    - Buying merch at stores only slightly skewed positively (BuyStor1)
    - Buying from sponsors heavily skewed to positive side (BuySpon1)
    - People intend to buy merch at the match (BuyMat1)
    - Most don't intend to buy merch at the store (BuyStor1)
    - People likely to purchase goods or services from sponsors rather than a non-sponsor (BuySpon1)
    - REGRESSION: lm(Buymer1 ~ BuyMat1 + BuySpon1)
    
**Questions**

+ seems like merch intentions are there

+ why do people feel this way about buying thru a sponsor?

```{r}
# merch intentions
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Merimp20
ggplot(data = merch_int, mapping = aes(x = Merimp20)) +
  geom_bar(),

# Merimp22
ggplot(data = merch_int, mapping = aes(x = Merimp22)) +
  geom_bar(), 

# Merimp24
ggplot(data = merch_int, mapping = aes(x = Merimp24)) +
  geom_bar(),

ncol = 2 )
```

**Comments**

    - affordability very important (merimp20)
    - quality very important( merimp22)
    - convenience of retail location not so important (merimp24)

**Questions**

+ How can we pair affordability and quality to the "Buy" variables above?

```{r}
# attendance intentions
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Cost3
ggplot(data = attendance_int, mapping = aes(x = Cost3)) +
  geom_bar(),

# Clink1
ggplot(data = attendance_int, mapping = aes(x = Clink1)) +
  geom_bar(), 

# Starfir1
ggplot(data = attendance_int, mapping = aes(x = Starfir1)) +
  geom_bar(),

# Attend17
ggplot(data = attendance_int, mapping = aes(x = Attend17)) + 
  geom_bar(),

# Seat1
ggplot(data = attendance_int, mapping = aes(x = Seat1)) + 
  geom_bar(),

# Ticket1
ggplot(data = attendance_int, mapping = aes(x = Ticket1)) + 
  geom_bar(),

ncol = 2 )
```

**Comments**

    - cost to attend is very important
    - CenturyLink field has some opposition to it, but better than Starfire
    - People don't seem to like Starfire as venue
    - People definitly intent on attending 2017 season
    - People seem to prefer general admission over assigned seating (Seat1)
    - Positive reviews of buying tickets online (Ticket1)

**Questions**

+ it seems that people prefer Century Link over Starfire, but it doesn't seem like people love Century Link. why not?

    - probably because the venue is too big
    - nobody likes paying for event parking 

+ why do people prefer general seating over assigned seating?
    
    - perhaps because there's not too many people at these games so you have the choice to sit as close as you want
    
```{r}
# attendance intentions
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Cost3
ggplot(data = attendance_int, mapping = aes(x = Cost3)) +
  geom_bar(),

# Clink1
ggplot(data = attendance_int, mapping = aes(x = Clink1)) +
  geom_bar(), 

# Starfir1
ggplot(data = attendance_int, mapping = aes(x = Starfir1)) +
  geom_bar(),

# Memorial
ggplot(data = attendance_int, mapping = aes(x = Expsat1)) +
  geom_bar(),

ncol = 2 )

```

**Comments**

    - It seems that the best experience is had at Memorial Stadium
        - Better than Century Link
        - Better than Starfire 
    - Propose hosting games at Memorial Stadium
    - Population seems to be happy with price point of tickets
    
## Base EDA Step 3: Multi-variate non-graphical

+ Focus on Website traffic for now since this was the most popular form of social media 

```{r}
# media intentions
# Contingency/cross table - Website on Gender

media_int %>% 
  tabyl(Website, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
media_int %>% 
  tabyl(Website, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

```

**Comments**

    - 2/3 of population that access Reign website are female. 1/3 male
    - most times to access the website for both male and female is 1

**Questions**

+ I wonder how female fans are treated/marketed to compared to male fans?

```{r}
# media intentions
# Contingency/cross table - Website on Race

media_int %>% 
  tabyl(Website, Race) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
media_int %>% 
  tabyl(Website, Race) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

```

**Comments**

    - Vast majority of website traffic comes from white people
    - Asians consist of 10% of website traffic
    
**Questions**

+ "other" has higher percentage than Native, Black, Hawaiian, and Prefer to answer. I wonder what these "other" categories are?

```{r}
# media intentions
# Contingency/cross table - Facebook on Gender

media_int %>% 
  tabyl(Facebook, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
media_int %>% 
  tabyl(Website, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

```

**Comments**

    - Similar results for Facebook as Website between males and females
    - Seems that people visit the FB page once in a week and that's good enough for them
    
```{r}
# media intentions
# Contingency/cross table - Website on SexOrient

media_int %>% 
  tabyl(Website, SexOrient) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
media_int %>% 
  tabyl(Website, SexOrient) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

```

**Comments**

    - Most website traffic comes from straight people
    - Gay/Lesbian community make up 20% of Reign website traffic

**Questions**

+ I wonder how "die hard" the Gay/Lesbian community is compared to the Straight community?


```{r}
# media intentions
# Contingency/cross table - EMAILS on Demographics

media_int %>% 
  tabyl(Media12, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
media_int %>% 
  tabyl(Media12, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

**Comments**

    - Emails more positively received by females
    - Neither males nor females dislike the emails
    
**Questions**

+ why are these emails so important?

```{r}
# media intentions
# Contingency/cross table - EMAILS on Demographics

media_int %>% 
  tabyl(Media12, SexOrient) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
media_int %>% 
  tabyl(Media12, SexOrient) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

**Comments**

    - all communities receive emails in a positive manner
    
```{r}
# media intentions
# Contingency/cross table - EMAILS on Demographics

media_int %>% 
  tabyl(Media12, Race) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
media_int %>% 
  tabyl(Media12, Race) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

**Comments** 

    - similar results as Website on Race
    - White people love these Reign emails, Asian people too
    - All demographics recieve emails in a positive manner

```{r}
# merch intentions
# Contingency/cross table

merch_int %>% 
  tabyl(Buymer1, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
merch_int %>% 
  tabyl(Buymer1, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

```

**Comments**

    - Females are more inclined to buy merch
    - Males are inclined to buy merch too, but some males have strong intentions to not buy merch
    
```{r}
# merch intentions
# Contingency/cross table

merch_int %>% 
  tabyl(Buymer1, SexOrient) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
merch_int %>% 
  tabyl(Buymer1, SexOrient) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

**Comments**

    - Every SexualOrientation intends on buying merch, except for the straight community
    - Straight community wants to buy merch, but some respondents felt negative towards it

```{r}
# attendance intentions
# Contingency/cross table

attendance_int %>% 
  tabyl(Attend17, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
attendance_int %>% 
  tabyl(Attend17, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

```

**Comments**

    - Some females don't intend on attending matches in 2017
    - All male respondents have intentions of attending matches in 2017

```{r}
# attendance intentions
# Contingency/cross table

attendance_int %>% 
  tabyl(Attend17, SexOrient) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
attendance_int %>% 
  tabyl(Attend17, SexOrient) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

**Comments**

    - Gay/Lesbian community intends on showing up in 2017
    - Gay/Lesbian and Straight communities Strongly Agree that they will be attending games in 2017

## Correlation matrix

```{r}
media_int_corr <- media_int %>% 
  select_if(is.numeric) %>%   # Use to select just the numeric variables
  cor() %>% 
  round(2) 

media_int_corr

# use corrplot for correlation matrix
corrplot(media_int_corr)

media_int_corr <- media_int %>% 
  select_if(is.numeric) %>%   # Use to select just the numeric variables
  cor()

corrplot(media_int_corr,
         method = "number",
         sig.level = 0.05,
         order = "original",
         diag = FALSE,
         type = "upper",
         tl.srt = 45,
         tl.col = "black")
```


```{r}
merch_int_corr <- merch_int %>% 
  select_if(is.numeric) %>%   # Use to select just the numeric variables
  cor() %>% 
  round(2) 

merch_int_corr

# use corrplot for correlation matrix
corrplot(merch_int_corr)
```


```{r}
attend_int_corr <- attendance_int %>% 
  select_if(is.numeric) %>%   # Use to select just the numeric variables
  cor() %>% 
  round(2) 

attend_int_corr

# use corrplot for correlation matrix
corrplot(attend_int_corr)
```

**Comments**

    - Good hints to see correlation between variables
    - Remember to not take these results too seriously
    
## Base EDA Step 4: Multi-variate graphical

- Bar graphs with multiple categorical variables

```{r}
# Code univariate bar graphs using grid.arrange so can see graphs together
# Demographics of Website users

race_ord <- c("White", "Asian", "Black/African American", "Native Hawaiian/Pacific Islander", "American Indian/Alaska Native")
sexorient_ord <- c("Gay/Lesbian", "Heterosexual", "Bisexual")

grid.arrange(
  
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = Website, fill = Gender)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),
  
  media_int %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = Website, fill = SexOrient)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),
  
  media_int %>%
    filter(Race %in% race_ord) %>% 
    ggplot(mapping = aes(x = Website, fill = Race)) + 
    geom_bar(position = "dodge") + 
    coord_flip(), 
  
  ncol = 1
)
```

**Comments**

    - Confirmed trends in demographics of website users
    
**Questions**

+ what does this tell me about Media Intentions?

    - Reign website is best way to communicate information to fans since it is the most widely accessed form of social media
    - All other social media outlets need to link to the website
    - website must ensure easy UI and ability to make purchases

```{r}
# Tile graph - need count
media_int %>% 
  group_by(Website, Gender) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(Website, Gender)) + 
  geom_tile(aes(fill = -count))
```

**Comments**

    - Most hits on website comes from Females, once a week
    
## Step 4.2: Quantitative

```{r}
# Code scatterplots using grid.arrange so can see all quant variables together
grid.arrange(
  # website on gender
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = Website, y = Gender)) + 
    geom_point(position = "jitter"),
  
  # website on SexOrient
  media_int %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = Website, y = SexOrient)) + 
    geom_point(position = "jitter"),
  
  # website on race
  media_int %>% 
    filter(Race %in% race_ord) %>% 
    ggplot(mapping = aes(x = Website, y = Race)) + 
    geom_point(position = "jitter"),
  
    ncol = 2
)
```

```{r}
# Code scatterplots using grid.arrange so can see all quant variables together
grid.arrange(
  # facebook on gender
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = Facebook, y = Gender)) + 
    geom_point(position = "jitter"),
  
  # facebook on SexOrient
  media_int %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = Facebook, y = SexOrient)) + 
    geom_point(position = "jitter"),
  
  # facebook on race
  media_int %>% 
    filter(Race %in% race_ord) %>% 
    ggplot(mapping = aes(x = Facebook, y = Race)) + 
    geom_point(position = "jitter"),
  
    ncol = 2
)

```


```{r}
# Code scatterplots using grid.arrange so can see all quant variables together
grid.arrange(
  # YouTube on gender
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = YouTube, y = Gender)) + 
    geom_point(position = "jitter"),
  
  # YouTube on SexOrient
  media_int %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = YouTube, y = SexOrient)) + 
    geom_point(position = "jitter"),
  
  # YouTube on race
  media_int %>% 
    filter(Race %in% race_ord) %>% 
    ggplot(mapping = aes(x = YouTube, y = Race)) + 
    geom_point(position = "jitter"),
  
    ncol = 2
)
```

## Categorical and Quantitative

```{r}
grid.arrange(
  # Website, Facebook, YouTube
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = Website, y = SexOrient, color = Gender)) + 
    geom_point(position = "jitter", alpha = 0.5) + 
    geom_smooth(method = "lm", se = FALSE), 
  
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = Facebook, y = SexOrient, color = Gender)) + 
    geom_point(position = "jitter", alpha = 0.5) + 
    geom_smooth(method = "lm", se = FALSE),
  
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = YouTube, y = SexOrient, color = Gender)) + 
    geom_point(position = "jitter", alpha = 0.5) + 
    geom_smooth(method = "lm", se = FALSE), 
  
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = Instagram, y = SexOrient, color = Gender)) + 
    geom_point(position = "jitter", alpha = 0.5) + 
    geom_smooth(method = "lm", se = FALSE), 
  
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = Twitter, y = SexOrient, color = Gender)) + 
    geom_point(position = "jitter", alpha = 0.5) + 
    geom_smooth(method = "lm", se = FALSE), 
  
  ncol = 2
  
  )

  
```

**Comments**

    - Social media usage dominated by Females
    - Not much interest from gay male community
    - Male interest primarily from straight community
    
**Questions**

+ What drives Female interest in the Reign?

```{r}
#  box plots
grid.arrange(
  # website on gender
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = Website, y = Gender)) + 
    geom_boxplot(),
  
  # Facebook on gender
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = Facebook, y = Gender)) + 
    geom_boxplot(),
  
  # YouTube on gender
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = YouTube, y = Gender)) + 
    geom_boxplot(),
    
  # IG on gender
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = Instagram, y = Gender)) + 
    geom_boxplot(),
  
  # Twitter on gender
  media_int %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = Twitter, y = Gender)) + 
    geom_boxplot()
  
  )
  
  
```

**Comments**

    - Website and YouTube accessed evenly by both Males and Females
    - Facebook, Instagram, and Twitter preferred by Females

# Research Question 2: Determine the factors that impact satisfaction (Performance, Outcome, Matchday Satisfaction).

```{r}
# Question 2 - Determine the factors that impact satisfaction (Performance, Outcome, Matchday Satisfaction).

# select variables that will answer research question 2
q2 <- soccer_updates %>% 
  select(Skill2, Success2, Drama4, Aggress3, Satperf3,
         Interest, IDnattm1, IDcomm2, Escape1, Skill2, Success2, Drama4, Aggress3, Socint1, RoleMod2, Satout2, Satperf3,
         Cost3, Promo3:Promo6, Travel1:Travel3, Travel5, Travel6, Seat1, 
         Matchsat:Consat5, Gender:Age)

# select and mutate variables that will answer Performance Satisfaction
performance_sat <- q2 %>% 
  select(c(1:5, Gender:Age)) 

# change data to numeric
performance_sat[, c(1:5)] <- sapply(performance_sat[, c(1:5)], as.numeric)

# select and mutate variables that will answer Outcome Satisfaction
outcome_sat <- q2 %>% 
  select(Interest:Satout2, Skill2:Satperf3, Gender:Age)

# change data to numeric
outcome_sat[, c(1:12)] <- sapply(outcome_sat[, c(1:12)], as.numeric)

# select and mutate variables that will answer Matchday Satisfaction
match_sat <- q2 %>% 
  select(Matchsat:Consat5, Gender:Age)

# change data to numeric
match_sat[, c(1:16)] <- sapply(match_sat[, c(1:16)], as.numeric)

match_sat <- match_sat %>% 
  tibble::rownames_to_column("Questions")
```

## Base EDA Step 1: Uni-variate non-graphical EDA

```{r}
# top of the dataset and look each subset
head(performance_sat)
vtable(performance_sat)

head(outcome_sat)
vtable(outcome_sat)

head(match_sat)
vtable(match_sat)
```

+ data appears to be tidy

    - data in each column is of the same variable type
    - no duplicate columns
    - each row is an individual's response to Reign survey
    - survey responses all uniform formatting (changed to cardinal responses and set as.numeric)
    - numeric variables and categorical
    
```{r}
# check descriptive statistics of media intentions
summary(performance_sat)
```

**Comments**

    - most variables seem to be close to normal distribution (Median = Mean)
    - when Mean > Median, that means fans were satisfied with the specific performance
    - all variables on -3 -> +3 scale
    
    
**Questions**

+ how can I gauge performance satisfaction with these variables? 

    - If highly positive, then people are satisfied

```{r}
# check descriptive statistics of media intentions
summary(outcome_sat)
```

**Comments**

    - when Mean > Median, that means fans were satisfied with the specific performance
    - all variables on -3 -> +3 scale
    
**Questions**

+ If response is highly positive, then people are satisfied

```{r}
# check descriptive statistics of media intentions
summary(match_sat)
```

**Comments**

    - when Mean > Median, that means fans were satisfied with the specific performance
    - all variables on 0 -> 7 scale
    - Neutral line is at 4
    
**Questions**

+ If response is above 4, then people are satisfied

## Base EDA Step 2: Uni-variate graphical EDA

- Examine each variable individually
- Examine how many observations in each variable

```{r}
# performance satisfaction - how satisfied
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Skill2
ggplot(data = performance_sat, mapping = aes(x = Skill2)) +
  geom_bar(),

# Success2
ggplot(data = performance_sat, mapping = aes(x = Success2)) +
  geom_bar(), 

# Drama4
ggplot(data = performance_sat, mapping = aes(x = Drama4)) +
  geom_bar(),

# Aggress3
ggplot(data = performance_sat, mapping = aes(x = Aggress3)) + 
  geom_bar(),

# Satperf3
ggplot(data = performance_sat, mapping = aes(x = Satperf3)) + 
  geom_bar(),

ncol = 2 )
```

**Comments**

    - Appears to have overall positive thoughts on performance variables
    - Higher counts on right side of 0 than on left side
    - Performance Satisfaction is high (Satperf3)
    - Excitement (Drama4), Aggression (Aggress3), Success (Success2), and Skill (Skill2) all contribute to Performance satisfaction  
    
**Questions**

+ Should I pull in demographics to this to see how different demographics feel about different aspects of the game?

```{r}
# outcome satisfaction - how satisfied
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Satisfaction of Outcome
ggplot(data = outcome_sat, mapping = aes(x = Satout2)) +
  geom_bar(),

# IDnattm1
ggplot(data = outcome_sat, mapping = aes(x = IDnattm1)) +
  geom_bar(), 

# IDcomm2
ggplot(data = outcome_sat, mapping = aes(x = IDcomm2)) +
  geom_bar(),

ncol = 2 )
```

**Comments**

    - Most respondents identify as fans of the National Team
    - Most respondents identify as part of the Seattle Community
    - Satisfaction of Outcome is slightly positive
    - Not many people thrilled about outcome, but nobody really hated it
    - Most people are big fans of the national team (IDnattm1)
    - Most people feel part of the Seattle community (IDcomm2)
    - Perhaps variables from Performance Satisfaction?
    - Overall experience at Memorial Stadium is high (Expsat1)
    - Friendliness of Arena Staff (Prsnsat1) and Security of Arena (Prsnsat2) are highly ranked
    
    
**Questions**

+ How can a team influence outcome satisfaction?

    - If most fans identify as part of the Seattle community and as fans of the national team, perhaps getting more national team players would help drive 

+ Perhaps I should bring in demographics to this as well to see who's satisfied or not

+ Is experience better at Memorial stadium or Clink or Starfire?


```{r}
# matchday satisfaction - how satisfied
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Satisfaction of match
ggplot(data = match_sat, mapping = aes(x = Matchsat)) +
  geom_bar(),

# Experience satisfaction at the stadium
ggplot(data = match_sat, mapping = aes(x = Expsat1)) +
  geom_bar(), 

# Satisfaction of staff from stadium
ggplot(data = match_sat, mapping = aes(x = Prsnsat1)) +
  geom_bar(),

# Satisfaction of stadium security
ggplot(data = match_sat, mapping = aes(x = Prsnsat2)) +
  geom_bar(),

ncol = 2 )
```

**Comments**

    - Match day satisfaction mostly positively satisfied
    - Experience at Memorial Stadium mostly positive
    - Friendliness of staff is positive (Prsnsat1)
    - People are mostly satisfied with security of the venue (Prsnsat2)

**Questions**

+ Need to pull in demographics to see who was satisfied for Match day and who was not

```{r}
# visualize likert data
match_sat %>% 
  group_by(Matchsat, Expsat1, Prsnsat1) %>% 
  summarize(n = n()) %>% 
  gather(Questions, Response, -c(n)) %>% 
  mutate(Response = as.factor(Response)) %>%  
  ggplot(mapping = aes(x = Questions, y = n, fill = Response)) + 
  geom_bar(stat = "identity", position = "fill") +
  coord_flip() +
    theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks = element_blank())
```

**Comments**

    - Many people were Very Satisfied with the match
    - Majority of people highly satisfied with all aspects of match day
    - Experience at Memorial Stadium was the weakest satisfaction variable about match day
    
**Questions**

+ Why the low satisfaction in Expsat1?

## Base EDA Step 3: Multi-variate non-graphical

```{r}
# outcome satisfaction
# Contingency/cross table - Performance Satisfaction

outcome_sat %>% 
  tabyl(Satout2, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
outcome_sat %>% 
  tabyl(Satout2, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

**Comments**

    - Same amount of females that are slightly dissatisfied as there are as slightly satisfied (13%)
    - Barely anyone feeling Very Dissatisfied or Very Satisfied
    - Many people feel neutral about the outcome
    
**Questions**

+ What plays into people's satisfaction of the outcome?

+ Are people more satisfied when the team wins?

```{r}
# outcome satisfaction
# Contingency/cross table - Performance Satisfaction

outcome_sat %>% 
  tabyl(Success2, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
outcome_sat %>% 
  tabyl(Success2, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

**Comments**

    - It seems that the success of the team influences the satisfaction of the match outcome
    - Success does not have the most weight as I assumed
    - People believe that the team wins more matches than it loses
    
**Questions**

+ How can I apply this to outcome satisfacation?


```{r}
# performance satisfaction
# Contingency/cross table - Performance Satisfaction

performance_sat %>% 
  tabyl(Satperf3, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
performance_sat %>% 
  tabyl(Satperf3, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

```{r}
# matchday satisfaction
# Contingency/cross table - Performance Satisfaction

match_sat %>% 
  tabyl(Matchsat, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
match_sat %>% 
  tabyl(Matchsat, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

**Comments**

    - Majority of people are satisfied with matchday experience
    - Most satisfaction coming from Females
    - Not too many people dissatisfied 
    
**Questions**

+ People seem to be satisfied with Matchday experience, yet not as satisfied for games at Memorial stadium


# Research Question 3: Determine ways to increase brand attitude.

```{r}
# Question 3 - Determine ways to increase brand attitude.

q3 <- soccer_updates %>% 
  select(Interest, BIRG1, RoleMod2, Posaff1, Negaff1, 
         Gender:Age)

q3[, c(1:5)] <- sapply(q3[, c(1:5)], as.numeric)
  

```

## Base EDA Step 1: Uni-variate non-graphical EDA

```{r}
# top of the dataset and look each subset
head(q3)
vtable(q3)
```

+ data appears to be tidy

    - data in each column is of the same variable type
    - no duplicate columns
    - each row is an individual's response to Reign survey
    - survey responses all uniform formatting (changed to cardinal responses and set as.numeric)
    - numeric variables and categorical variables
    
```{r}
# check descriptive statistics of media intentions
summary(media_int)

```


**Comments**

    - most variables seem to be right skewed since mean >> median
        - scale for most variables is -3 -> 3, so makes sense that 0 is median for many
        - median more representative than mean
    - lots of NA's that will need to be filtered out
    
**Questions**

+ how can I gauge ways to increase brand attitude with these variables?

    - Account for role models on the team, positive and negative affirmation, and break it out by demographics

## Base EDA Step 2: Uni-variate graphical EDA

- Examine each variable individually
- Examine how many observations in each variable

```{r}
# increase brand attitude
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Interest
ggplot(data = q3, mapping = aes(x = Interest)) +
  geom_bar(),

# BIRG1
ggplot(data = q3, mapping = aes(x = BIRG1)) +
  geom_bar(), 

# RoleMod2
ggplot(data = q3, mapping = aes(x = RoleMod2)) +
  geom_bar(),

# Posaff1
ggplot(data = q3, mapping = aes(x = Posaff1)) + 
  geom_bar(),

# Negaff1
ggplot(data = q3, mapping = aes(x = Negaff1)) + 
  geom_bar(),

ncol = 2 )
```

**Comments**

    - Majority of people are positively interested in the team
    - More sentiment around showing others about team support/association (BIRG1)
    - Majority of people believe the players are positive role models for children
    - Most people feel positive about Reign 2016 season
    - Most people do not feel negative about Reign 2016 season
    
```{r}
# visualize likert data
q3 %>% 
  group_by(BIRG1, RoleMod2, Posaff1, Negaff1) %>% 
  summarize(n = n()) %>% 
  gather(Questions, Response, -c(n)) %>% 
  mutate(Response = as.factor(Response)) %>%  
  ggplot(mapping = aes(x = Questions, y = n, fill = Response)) + 
  geom_bar(stat = "identity", position = "fill") +
  coord_flip() +
    theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks = element_blank())
```

**Comments**

    - There is a tiny number of respondents that would hide that their association with the Reign (BIRG1)
    - Vast majority of respondents have positive sentiments toward the team and branding
    - Reign seem to be like a good team to be role models to children
    - Having the players serve as good role models to children can help improve brand attitude (RoleMod2)
        - REGRESSION: lm(Interest ~ RoleMod2 + Gender)
    
    
## Correlation matrix

```{r}
q3_corr <- q3 %>% 
  select_if(is.numeric) %>%   # Use to select just the numeric variables
  cor() %>% 
  round(2) 

q3_corr

# use corrplot for correlation matrix
corrplot(q3_corr)

q3_corr <- q3 %>% 
  select_if(is.numeric) %>%   # Use to select just the numeric variables
  cor()

corrplot(q3_corr,
         method = "number",
         sig.level = 0.05,
         order = "original",
         diag = FALSE,
         type = "upper",
         tl.srt = 45,
         tl.col = "black")
```

**Comments**

    - Good hints to see correlation between variables
    - Remember to not take these results too seriously
    - Role Model is only correlation that's registering. Gotta be good role models to the kiddos!
    
**Questions**

+ Not sure if I'm doing something that broke this corr chart. Why is everything else NA when they're all numeric? Perhaps too small to register?

## Base EDA Step 4: Multi-variate graphical

- Bar graphs with multiple categorical variables

```{r}
# Code univariate bar graphs using grid.arrange so can see graphs together
# Increase brand attitude

grid.arrange(
  
  q3 %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = Interest, fill = Gender)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),
  
  q3 %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = BIRG1, fill = Gender)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),
  
  q3 %>%
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = RoleMod2, fill = Gender)) + 
    geom_bar(position = "dodge") + 
    coord_flip(), 
  
  ncol = 1
)
```

**Comments**

    - Females seem to have the most pride in brand attitude
    - Females believe Reign team are good role models to the kids
    
**Questions**

+ How can Reign convince Male fans to adopt the brand and identify as Reign fans?

# Research Question 4: Investigate purchasing habits of corporate partner products. 

```{r}
# Question 4 - Investigate purchasing habits of corporate partner products. 

q4 <- soccer_updates %>% 
  # select businesses that sponsor the Reign
  select(Purchs1:Purchs10, Spnbuy1:Spnbuy10, Gender:Age) 

purch_habits <- q4 %>% 
  select(Purchs1:Purchs10) %>%
  rename(Subaru_purch = Purchs1,
         Microsoft_purch = Purchs2, 
         Pepsi_purch = Purchs3, 
         BECU_purch = Purchs4, 
         Chihuly_purch = Purchs5, 
         Hardrock_purch = Purchs6, 
         Health_Warrior_purch = Purchs7, 
         Hyatt_purch = Purchs8, 
         Kraken_Congee_purch = Purchs9, 
         Ruffneck_Scarves_purch = Purchs10) 

q4[, c(1:10)] <- sapply(q4[, c(1:10)], as.factor)
    

# if you need the grouped dataset

purch_habits_grouped <- purch_habits %>% 
  pivot_longer(cols = everything()) %>% 
  group_by(name) %>% 
  summarise(count_n = n())

# grouping by sponsor
sponsor <- q4 %>% 
  select(Spnbuy1:Spnbuy10) %>% 
  rename(Subaru_spn = Spnbuy1, 
         Microsoft_spn = Spnbuy2, 
         Pepsi_spn = Spnbuy3, 
         BECU_spn = Spnbuy4, 
         Chihuly_spn = Spnbuy5, 
         Hardrock_spn = Spnbuy6, 
         Health_Warrior_spn = Spnbuy7, 
         Hyatt_spn = Spnbuy8, 
         Kraken_Congee_spn = Spnbuy9, 
         Ruffneck_Scarves_spn = Spnbuy10) %>% 
  pivot_longer(cols = everything()) %>% 
  group_by(name) %>% 
  summarise(value = mean(value, na.rm = TRUE))

```

## Base EDA Step 1: Uni-variate non-graphical EDA

```{r}
# top of the dataset and look each subset
head(q4)
vtable(q4)

```

+ data appears to be tidy

    - data in each column is of the same variable type
    - no duplicate columns
    - each row is an individual's response to Reign survey
    - survey responses all uniform formatting (changed to cardinal responses and set as.numeric)
    - numeric variables and categorical

```{r}
# check descriptive statistics of q4
summary(q4)
```

**Comments**

    - 4 is neutral line in these survey questions
        - scale is from 1 to 7
    - Appears that most questions were answered as neutral or negatively
    
**Questions**

+ how can I gauge purchasing habits with these variables?

    - If it is seen that people are more satisfied with a particular sponsor, then that sponsor should become Reign's biggest champion
    - Success from a sponsor partnership will spur interest with more sponsors
    - More sponsors will enable more fans to get involved which will lead to an increase in brand attitude
    - Partnerships with sponsors should be good for both partners

## Base EDA Step 2: Uni-variate graphical EDA

- Examine each variable individually
- Examine how many observations in each variable

```{r}
# Purchase habits
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Spnbuy variables
ggplot(data = q4, mapping = aes(x = Spnbuy1)) +
  geom_bar(),

ggplot(data = q4, mapping = aes(x = Spnbuy2)) +
  geom_bar(), 

ggplot(data = q4, mapping = aes(x = Spnbuy3)) +
  geom_bar(),

ggplot(data = q4, mapping = aes(x = Spnbuy4)) + 
  geom_bar(),


ggplot(data = q4, mapping = aes(x = Spnbuy5)) + 
  geom_bar(),

ggplot(data = q4, mapping = aes(x = Spnbuy6)) +
  geom_bar(),

ggplot(data = q4, mapping = aes(x = Spnbuy7)) +
  geom_bar(), 

ggplot(data = q4, mapping = aes(x = Spnbuy8)) +
  geom_bar(),

ggplot(data = q4, mapping = aes(x = Spnbuy9)) + 
  geom_bar(),

ggplot(data = q4, mapping = aes(x = Spnbuy10)) + 
  geom_bar(),

ncol = 4 )
```

**Comments**

    - Microsoft (Spnbuy2) seems to have the most influence out of the sponsors
    - BECU (Spnbuy4) comes in second after MSFT
    - Hardrock Caf (Spnbuy6), Health Warrior (Spnbuy7), and Hyatt House (Spnbuy8)- doesn't influence purchasing habits by much
    - Roughneck Scarves seems to have a decent following (Spnbuy10)
        - Probably because everyone buys scarves to wear on matchday
    - It doesn't seem that any of these sponsors have a particular amount of influence over behaviors
    
+ Kraken Congee seems to have a little more influence, possibly thanks to Reign popularity with Asian demographic

    - kraken congee is now closed as of 2021 :'(
    
**Questions**

+ What kind of "deals" would entice people to get behind a specific sponsor?

+ These sponsors aren't really that habit forming for repeat purchases from fans (other than Pepsi). It seems that the Reign need to choose different company sponsors to really influence customer behavior

    - People don't buy subarus all the time
    - People don't go to Chihuly or Hardrock Cafe more than they really have to
    - Fans probably don't need a sponsorship from Hyatt House if they go to Reign home games and they already live in Seattle

## Base EDA Step 3: Multi-variate non-graphical

+ Focus on Website traffic for now since this was the most popular form of social media 

```{r}
# purchasing habits
# Contingency/cross table - Website on Gender

q4 %>% 
  tabyl(Spnbuy2, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
q4 %>% 
  tabyl(Spnbuy2, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

```

**Comments**

    - Males seem to be motivated my Microsoft more than other brand sponsorships (35%)
    - Still much higher participation from Female respondents

**Questions**

+ I wonder how female fans are treated/marketed to compared to male fans?

```{r}
q4 %>% 
  tabyl(Spnbuy10, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
q4 %>% 
  tabyl(Spnbuy10, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

    
## Base EDA Step 4: Multi-variate graphical

- Bar graphs with multiple categorical variables

```{r}
# Code univariate bar graphs using grid.arrange so can see graphs together
# influencing purchasing habits

grid.arrange(
  
  q4 %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = Spnbuy2, fill = Gender)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),
  
  q4 %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = Spnbuy2, fill = SexOrient)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),
  
  q4 %>%
    filter(Race %in% race_ord) %>% 
    ggplot(mapping = aes(x = Spnbuy2, fill = Race)) + 
    geom_bar(position = "dodge") + 
    coord_flip(), 
  
  ncol = 1
)
```

**Comments**

    - Biggest market: straight, white, females
    
**Questions**

+ what does this tell me about purchasing habits?

    - Largest market is straight white women
        - Seek sponsorships from businesses that target these types of people (perhaps something like Target!)
    - Second largest market is the Gay/Lesbian community
        - Seek sponsorships from businesses that support the gay community (perhaps something like Rudy's barbershop)

```{r}
# Tile graph heat map - need count
q4 %>% 
  group_by(Spnbuy2, Gender) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(Spnbuy2, Gender)) + 
  geom_tile(aes(fill = -count))
```

**Comments**

    - Females are mostly Neutral or not strongly influenced by Microsoft sponsorship
    - Males are slightly more influenced

```{r}
# visualize likert data
q4 %>% 
  group_by(Spnbuy2, Spnbuy10) %>% 
  summarize(n = n()) %>% 
  gather(Questions, Response, -c(n)) %>% 
  mutate(Response = as.factor(Response)) %>%  
  ggplot(mapping = aes(x = Questions, y = n, fill = Response)) + 
  geom_bar(stat = "identity", position = "fill") +
  coord_flip() +
    theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks = element_blank())
```

**Comments**

    - Pretty even distribution for these two variables
    - More positive satisfaction for Microsoft (Spnbuy2)
    - Pretty even for Ruffneck Scarves (Spnbuy10)


# Research Question 5: Investigate ways to improve gameday experience.

```{r}
# Question 5 - Investigate ways to improve gameday experience.

q5 <- soccer_updates %>% 
  select(Matchsat:Consat7, Gender:Age)

q5[, c(1:17)] <- sapply(q5[, c(1:17)], as.numeric)

```

## Base EDA Step 1: Uni-variate non-graphical EDA

```{r}
# top of the dataset and look each subset
head(q5)
vtable(q5)

```

+ data appears to be tidy

    - data in each column is of the same variable type
    - no duplicate columns
    - each row is an individual's response to Reign survey
    - survey responses all uniform formatting (changed to cardinal responses and set as.numeric)
    - numeric and categorical variables

```{r}
# check descriptive statistics of q5
summary(q5)
```

**Comments**

    - 4 is neutral line in these survey questions
        - scale is from 1 to 7
    - Appears that most questions were answered as positively or neutral
    
**Questions**

+ how can I gauge gameday experience with these variables?

    - Look for the most negative ratings for a facet of the gameday experience and focus to improve that
    - Find highest rating facet and highlight this

## Base EDA Step 2: Uni-variate graphical EDA

- Examine each variable individually
- Examine how many observations in each variable

```{r}
# gameday experience
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Satisfaction variables
ggplot(data = q5, mapping = aes(x = Matchsat)) +
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Expsat1)) +
  geom_bar(), 

ggplot(data = q5, mapping = aes(x = Prsnsat1)) +
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Autgsat1)) + 
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Prsnsat2)) + 
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Prsnsat3)) +
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Consat3)) +
  geom_bar(), 

ggplot(data = q5, mapping = aes(x = Consat4)) +
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Consat1)) + 
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Consat9)) + 
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Consat6)) + 
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Consat8)) + 
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Beersat1)) + 
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Consat2	)) + 
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Prsnsat4)) + 
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Consat5)) + 
  geom_bar(),

ggplot(data = q5, mapping = aes(x = Consat7)) + 
  geom_bar(),

ncol = 5 )
```

**Comments**

    - Consat2 - variety of food options - lots of negativity
    - Consat3 - Current concession offerings - lots of negativity
    - Consat8 - people seem to love the convenience of concession location
    - Prsnsat1 - friendliness of arena staff is very well received
    - Match satisfaction likely influences gameday experience (Matchsat)
    - People don't seem to mind games at Memorial stadium (Expsat1)
    - Friendliness of staff has high ratings (Prsnsat1)
    - Variety of food options (Consat2) has negative ratings.
        - Strategy to improve variety of food options would improve gameday experience. This makes sense
        - Convenience of concession location is positively received
    - Shocking to see such flat results for Location of Beer Garden (Beersat1)
        - Perhaps this makes sense since majority of fans are straight women?
        - Reign needs to put up a Spiked Seltzer garden or Rose fountain
    
**Questions**

+ Would it be possible to have food trucks in the parking lot? This would improve food variety but profits would need to be split

## Base EDA Step 3: Multi-variate non-graphical

+ Focus on factors that go into gameday experience

```{r}
# gameday experience
# Contingency/cross table

q5 %>% 
  tabyl(Consat2, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
q5 %>% 
  tabyl(Consat2, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

q5 %>% 
  tabyl(Consat2, SexOrient) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
q5 %>% 
  tabyl(Consat2, SexOrient) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

```

**Comments**

    - Only slightly satisfied with food variety
    - Food variety had the highest amount of negative responses out of this data
    - Not many people loved the options, but not many people hated it either
        -Improving food options and satisfying hangriness could help boost gameday experience

**Questions**

+ I wonder what people would prefer to eat at a game


    
## Base EDA Step 4: Multi-variate graphical

- Bar graphs with multiple categorical variables

```{r}
# Code univariate bar graphs using grid.arrange so can see graphs together
# influencing gameday experience

grid.arrange(
  
  q5 %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = Consat2, fill = Gender)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),
  
  q5 %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = Consat2, fill = SexOrient)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),
  
  q5 %>%
    filter(Race %in% race_ord) %>% 
    ggplot(mapping = aes(x = Consat2, fill = Race)) + 
    geom_bar(position = "dodge") + 
    coord_flip(), 
  
  ncol = 1
)
```

**Comments**

    - Biggest market: straight, white, females
    - Some people are pretty unhappy about the food options
    
**Questions**

+ what does this tell me about gameday experience?

    - Need to feed the fans quality food
    - Food purchases can contribute to profits

```{r}
# Tile graph heat map - need count
q5 %>% 
  group_by(Consat2, Gender) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(Consat2, Gender)) + 
  geom_tile(aes(fill = -count))
```

**Comments**

    - Both males and females are very unsatisfied with variety of food at the game
    - 4 is neutral

```{r}
# visualize likert data
q5 %>% 
  group_by(Consat2, Consat4) %>% 
  summarize(n = n()) %>% 
  gather(Questions, Response, -c(n)) %>% 
  mutate(Response = as.factor(Response)) %>%  
  ggplot(mapping = aes(x = Questions, y = n, fill = Response)) + 
  geom_bar(stat = "identity", position = "fill") +
  coord_flip() +
    theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks = element_blank())
```

**Comments**

    - Majority of people feel negatively toward Variety of food (Consat2) and price point of food (Consat4)
    
**Questions**

+ What food options would people prefer to see offered at the game


# Research Question 6: Identify viable market segments

```{r}
# Question 6 - Identify viable market segments

q6 <- soccer_updates %>% 
  select(Gender:Zipcode)

q6[, c(5:22)] <- sapply(q6[, c(5:22)], as.numeric)

```

## Base EDA Step 1: Uni-variate non-graphical EDA

```{r}
# top of the dataset and look each subset
head(q6)
vtable(q6)

```

+ data appears to be tidy

    - data in each column is of the same variable type
    - no duplicate columns
    - each row is an individual's response to Reign survey
    - survey responses all uniform formatting (changed to cardinal responses and set as.numeric)
    - numeric and categorical variables

```{r}
# check descriptive statistics of q6
summary(q6)
```

**Comments**

    - There are several binary variables here, unlike the rest of the research questions
        - The higher the mean, the more people identify as YES for the survey question
    - GameTime variables - the higher the number, the later in the week and later in the day the game times are
    - More Married/Partnered people than there are Single people
    - Most people hold college degrees or graduate degrees
    
    
**Questions**

+ how can I gauge market segments with these variables?

    - If there are Reign fans that identify as fans of other Seattle sports teams, perhaps do promos where you can support both teams
        - Sounders and Reign are doing a joint event in late August 2021
        - Promote the Reign at other sporting events
    - Schedule games during the times of most availability

## Base EDA Step 2: Uni-variate graphical EDA

- Examine each variable individually
- Examine how many observations in each variable

```{r}
# market segments
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# fans of other teams/events and most popular match day/times
ggplot(data = q6, mapping = aes(x = SeaEvnt1)) +
  geom_bar(),

ggplot(data = q6, mapping = aes(x = SeaEvnt2)) +
  geom_bar(), 

ggplot(data = q6, mapping = aes(x = SeaEvnt3)) +
  geom_bar(),

ggplot(data = q6, mapping = aes(x = SeaEvnt4)) + 
  geom_bar(),

ggplot(data = q6, mapping = aes(x = SeaEvnt5)) + 
  geom_bar(),

ggplot(data = q6, mapping = aes(x = SeaEvnt6)) +
  geom_bar(),

ggplot(data = q6, mapping = aes(x = SeaEvnt7)) +
  geom_bar(), 

ggplot(data = q6, mapping = aes(x = SeaEvnt8)) +
  geom_bar(),

ggplot(data = q6, mapping = aes(x = SeaEvnt9)) + 
  geom_bar(),

ggplot(data = q6, mapping = aes(x = GameTim1)) + 
  geom_bar(),

ggplot(data = q6, mapping = aes(x = GameTim2)) + 
  geom_bar(),

ggplot(data = q6, mapping = aes(x = GameTim3)) + 
  geom_bar(),

ggplot(data = q6, mapping = aes(x = GameTim4)) + 
  geom_bar(),

ggplot(data = q6, mapping = aes(x = GameTim5)) + 
  geom_bar(),

ggplot(data = q6, mapping = aes(x = GameTim6)) + 
  geom_bar(),

ggplot(data = q6, mapping = aes(x = GameTim7)) + 
  geom_bar(),

ncol = 5 )
```

**Comments**

    - Biggest synergies would come from Sounders and Mariners as these are the highest attended team events
    - Little support coming from SeaEvnt5 - SeaEvent9
    - Most popular game time by far is Wednesday evenings
        - This is surprising
        - I guess the Reign is a weekday activity and people don't want to spend their weekends for it?
    
**Questions**

+ What does this tell me about market segments?

    - Fans who support the Sounders and the Mariners are likely to support the Reign
    - Wednesday night games are the most popular
        - This makes it tough for families with children to go 
        
+ White, Heterosexual Females were seen as the biggest market for Reign supporters. What does this tell me?

    - Friends and boyfriends probably attend with them
    - They don't care much to drink beer in a beer garden
    - They want more variety in food options
    
```{r}
# market segments
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(
# market segment variables
ggplot(data = q6, mapping = aes(x = Marital)) +
  geom_bar(),

ggplot(data = q6, mapping = aes(x = Educat)) +
  geom_bar(),

q6 %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = Gender)) + 
    geom_bar(position = "dodge"), 

q6 %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = SexOrient)) + 
    geom_bar(position = "dodge"), 

q6 %>% 
    filter(Race %in% race_ord) %>% 
    ggplot(mapping = aes(x = Race)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),

ncol = 2)
```

**Comments**

    - Top segments:
        - Married/Partnered
        - College degree and/or Graduate Degree
        - Female
        - Heterosexual
        - White
    - Target market: White, college educated, married/partnered, heterosexual females

## Base EDA Step 3: Multi-variate non-graphical

+ Focus on factors that go into market segment

```{r}
# market segment
# Contingency/cross table

q6 %>% 
  tabyl(SeaEvnt3, Gender) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
q6 %>% 
  tabyl(SeaEvnt3, Gender) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

q6 %>% 
  filter(SexOrient %in% sexorient_ord) %>% 
  tabyl(Marital, SexOrient) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

# Proportion contingency/cross table
q6 %>% 
  filter(SexOrient %in% sexorient_ord) %>% 
  tabyl(Marital, SexOrient) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) %>%  # round decimals
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

```

**Comments**

    - Married/Partnered:
        - 11% of married/partnered couples are Gay/Lesbian
        - 50% married/partnered couples are straight
        - 2% bisexual
    - Single people:
        - 21% straight
        - 10% gay/lesbian
        - 4% bisexual
    - Female:
        - 33% of females have attended a Sounders game

**Questions**

+ I thought there would be more of a following from Gay/Lesbian community?

+ What does straight people in relationships making up majority of the market tell me?

    
## Base EDA Step 4: Multi-variate graphical

- Bar graphs with multiple categorical variables

```{r}
# Code univariate bar graphs using grid.arrange so can see graphs together
# influencing gameday experience

grid.arrange(
  
  q6 %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = SeaEvnt3, fill = Gender)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),
  
  q6 %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = SeaEvnt3, fill = SexOrient)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),
  
  q6 %>%
    filter(Race %in% race_ord) %>% 
    ggplot(mapping = aes(x = SeaEvnt3, fill = Race)) + 
    geom_bar(position = "dodge") + 
    coord_flip(), 
  
    q6 %>% 
    filter(str_detect(Gender, "ale")) %>% 
    ggplot(mapping = aes(x = SeaEvnt4, fill = Gender)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),
  
  q6 %>% 
    filter(SexOrient %in% sexorient_ord) %>% 
    ggplot(mapping = aes(x = SeaEvnt4, fill = SexOrient)) + 
    geom_bar(position = "dodge") + 
    coord_flip(),
  
  q6 %>%
    filter(Race %in% race_ord) %>% 
    ggplot(mapping = aes(x = SeaEvnt4, fill = Race)) + 
    geom_bar(position = "dodge") + 
    coord_flip(), 
  
  ncol = 2
)
```

**Comments**

    - Biggest market: straight, white, females
    - Female Reign attendees have most likely attended a Sounders game
    - More likely for a female fan to attend a Sounders game than a Mariner's game
    - Unlikely for a straight person to have attended a Mariner's game
    
**Questions**

+ what does this tell me about market segments?

    - People who are fans of the Reign are likely fans of the Sounders
        - Fans of soccer
        - REGRESSION: lm(SeaEvnt3 ~ Interest + Gender)

```{r}
# Tile graph heat map - need count
q6 %>% 
  group_by(SeaEvnt3, Gender) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(SeaEvnt3, Gender)) + 
  geom_tile(aes(fill = -count))
```

**Comments**

    - It is likely that the Female cohort also attend Sounders games

```{r}
# visualize likert data
q6 %>% 
  group_by(SeaEvnt3, SeaEvnt4) %>% 
  summarize(n = n()) %>% 
  gather(Questions, Response, -c(n)) %>% 
  mutate(Response = as.factor(Response)) %>%  
  ggplot(mapping = aes(x = Questions, y = n, fill = Response)) + 
  geom_bar(stat = "identity", position = "fill") +
  coord_flip() +
    theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks = element_blank())
```

**Comments**

    - Majority of people feel negatively toward Variety of food (Consat2) and price point of food (Consat4)
    
**Questions**

+ What food options would people prefer to see offered at the game

```{r}
q6 %>% 
  group_by(GameTim1, GameTim2, GameTim3) %>% 
  summarize(n = n()) %>% 
  gather(Questions, Response, -c(n)) %>% 
  mutate(Response = as.factor(Response)) %>%  
  ggplot(mapping = aes(x = Questions, y = n, fill = Response)) + 
  geom_bar(stat = "identity", position = "fill") +
  coord_flip() +
    theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks = element_blank())
```

**Comments**

    - Sunday Evenings is the most popular (Gametime=7)

