---
title: "Influencing Reign FC brand attitude and gameday experience"
author: Andrew Nalundasan
date: August 27, 2021
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo = FALSE}
# Course: OMSBA 5210
# Purpose: DTC - Slides
# Date: August 27, 2021
# Author: Andrew Nalundasan
```

```{r echo = FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 

# NOTE, DO NOT CLEAR PACKAGES, IF YOU DO IT WILL NOT RUN
```


```{r message=FALSE, include=FALSE}

library(ggannotate)    # annotation tool
library(scales)        # to get $ and , on axis in graph
library(tidyverse)     # contains ggplot2, dplyr, and several other packages
library(vtable)        # NHK special
library(gghighlight)   # visual formatting - highlights
library(ggiraph)       # ggiraph
```


```{r include=FALSE}
# read data into environment and assign to object
soccer <- read_csv("../02_raw_data/Seattle_Reign.csv")

# make updates to data here so can pull from cleaned data
soccer_updates <- soccer %>% 
  # transform Interest responses to numeric
  mutate(Interest = str_replace_all(Interest, "I have a small amount of interest", "1")) %>% 
  mutate(Interest = str_replace_all(Interest, "I consider myself to be a low-level fan of this team", "2")) %>% 
  mutate(Interest = str_replace_all(Interest, "I consider myself to be a moderate fan of this team", "3")) %>% 
  mutate(Interest = str_replace_all(Interest, "I consider myself to be a loyal fan of this team", "4")) %>% 
  mutate(Interest = str_replace_all(Interest, "I live and die with this team", "5")) %>% 
  # make Interest a factor
  mutate(Interest = as.factor(Interest)) %>% 
  # media variables
  mutate(Media1 = str_sub(Media1, -2)) %>% 
  mutate(Media3 = str_sub(Media3, -2)) %>%
  mutate(Media4 = str_sub(Media4, -2)) %>%
  mutate(Media5 = str_sub(Media5, -2)) %>%
  mutate(Media6 = str_sub(Media6, -2)) %>%
  mutate(Media12 = str_sub(Media12, -2)) %>%
  mutate(Media7a = str_sub(Media7a, -2)) %>%
  mutate(Media7b = str_sub(Media7b, -2)) %>% 
  # sponsor variables
  mutate(across(starts_with('Spnbuy'), function(x) str_sub(x, -1))) %>% 
  mutate(across(starts_with('Spnbuy'), function(x) as.numeric(x))) %>% 
  # grab last 2 characters of string and change class to numeric
  mutate(Travel1 = str_sub(Travel1, -2)) %>%  
  mutate(Travel1 = as.numeric(Travel1)) %>% 
  mutate(Travel2 = str_sub(Travel2, -2)) %>%
  mutate(Travel2 = as.numeric(Travel2)) %>% 
  mutate(Travel3 = str_sub(Travel3, -2)) %>% 
  mutate(Travel3 = as.numeric(Travel3)) %>% 
  mutate(Seat1 = str_to_title(Seat1)) %>% 
  # grab last 2 characters of Promo variables
  mutate(across(starts_with('Promo'), function(x) str_sub(x, -2))) %>% 
  mutate(across(starts_with('Promo'), function(x) as.numeric(x)))
  
# change all character responses to numeric scale to analyze as likert scale
soccer_updates[soccer_updates == "Strongly disagree"] <- "-3"
soccer_updates[soccer_updates == "Strongly Disagree"] <- "-3"
soccer_updates[soccer_updates == "Disagree"] <- "-2"
soccer_updates[soccer_updates == "Somewhat disagree"] <- "-1" 
soccer_updates[soccer_updates == "Somewhat Disagree"] <- "-1" 
soccer_updates[soccer_updates == "Neutral"] <- "0" 
soccer_updates[soccer_updates == "Somewhat agree"] <- "1"
soccer_updates[soccer_updates == "Somewhat Agree"] <- "1"
soccer_updates[soccer_updates == "Agree"] <- "2" 
soccer_updates[soccer_updates == "Strongly agree"] <- "3"
soccer_updates[soccer_updates == "Strongly Agree"] <- "3"
soccer_updates[soccer_updates == "Very Unimportant"] <- "1"
soccer_updates[soccer_updates == "Very Important"] <- "7"
soccer_updates[soccer_updates == "Prefer not to answer"] <- "Undisclosed"
soccer_updates[soccer_updates == "Very Dissatisfied"] <- "1"
soccer_updates[soccer_updates == "Very Satisfied"] <- "7"
soccer_updates[soccer_updates == "Single"] <- "1"
soccer_updates[soccer_updates == "Married/Partnered"] <- "2"
soccer_updates[soccer_updates == "Some High School"] <- "1"
soccer_updates[soccer_updates == "High School Graduate"] <- "2"
soccer_updates[soccer_updates == "Some College"] <- "3"
soccer_updates[soccer_updates == "College Graduate"] <- "4"
soccer_updates[soccer_updates == "Graduate Degree"] <- "5"
soccer_updates[soccer_updates == "Other"] <- "6"
```

```{r eval=FALSE, include=FALSE}

# Full screen intro of MY FACE

# Hello everyone. Thank you for this opportunity to present to you today. My name is Andrew Nalundasan, and I will be covering the findings from my recent analysis regarding potential methods of increasing brand attitude and enhancing gameday experience for the Reing FC. In this video, I will give a brief overview of the data set and the analyses performed, I will speak about the findings and recommendations that came out of the analyses, and I'll wrap it up with our key takeaways. 

# Start sharing screen and begin presentation
```


Introduction
===============================================

+ The Data:

    + Survey distributed online via email list provided by Seattle Reign FC 
    + 684 respondents
    + Data has been anonymized - no privacy concerns for Reign FC fans

+ Insights into respondent behaviors and levels of satisfaction

    + People are generally proud to be associated with the Reign
    + People seem to prefer match day experience at Memorial Stadium
        + Indifferent about Century Link 
        + Negative sentiments for Starfire 
        

Team of good role models helps drive brand attitude
===============================================

<div style="float: left; width: 35%;">

+ Brand attitude was found to be highly correlated with sentiments about the Reign being good role models to children

+ Reign FC should have policy for team members to avoid the negative spotlight 

+ Cultivating a strong fanbase in today's children will lead to strong fanbase in the future

</div>

<div style="float: left; width: 65%;">

```{r echo=FALSE, message=FALSE, warning=FALSE}
# visual telling story about brand attitude

# wrangle data
q3 <- soccer_updates %>% 
  select(Interest, BIRG1, RoleMod2, Posaff1, Negaff1, 
         Gender:Age)

q3[, c(1:5)] <- sapply(q3[, c(1:5)], as.numeric)

brand_att <- q3 %>% 
  filter(str_detect(Gender, "ale"))

# build the viz
cb_palette <- c("#cccccc", "#00aedb")

q3_vis <- brand_att %>% 
  group_by(BIRG1, RoleMod2) %>% 
  summarize(count = n()) %>% 

  ggplot(aes(BIRG1, RoleMod2)) + 
  geom_tile_interactive(aes(fill = -count)) +  
  scale_fill_distiller(palette = "RdPu") +
  
  #scale_x_continuous(breaks = c("Strongly Disagree", "Neutral", "Strongly Agree")) +
  coord_flip() +
  theme_classic() + 
  theme(axis.line.x = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") + 
  labs(x = "", 
       y = "",
       title = "Major support from people that believe Reign are role models",
       subtitle = "Reign can have a positive impact to children and the community") + 
  
  # annotations
  geom_text(data = data.frame(x = 3.45013154997636, y = -3.50221388195219, label = "Most Pride"),
            mapping = aes(x = x, y = y, label = label),
            hjust = 0L, colour = "#990066", fontface = 2, inherit.aes = FALSE) + 
  
  geom_text(data = data.frame(x = -2.06558111093393, y = -3.50221388195219, label = "Least Pride"),
            mapping = aes(x = x, y = y, label = label),
            hjust = 0L, colour = "#FFCCCC", fontface = 2, inherit.aes = FALSE) +
  
  geom_text(data = data.frame(x = -3.80993805601707, y = -3.09115165591085, label = "Bad Role Model"),
            mapping = aes(x = x, y = y, label = label),
            hjust = 0.4, colour = "#FFCCCC", fontface = 2, inherit.aes = FALSE) + 

  geom_text(data = data.frame(x = -3.70922298458263, y = 2.94268974345045, label = "Great Role Model"),
            mapping = aes(x = x, y = y, label = label),
            colour = "#990066", fontface = 2, inherit.aes = FALSE)

ggiraph(ggobj = q3_vis)

```


</div>

Food options help drive gameday experience
===============================================

<div style="float: left; width: 35%;">

+ Fans are more satisfied with more food options

+ Satisfaction in food variety influences gameday experience

+ Gameday experience can be enhanced with the right food options

+ Gameday experience at Memorial Stadium is preferred over Century Link and Starfire

</div>

<div style="float: left; width: 65%;">

```{r echo=FALSE, message=FALSE, warning=FALSE}
# improve gameday experience
# wrangle data

q5 <- soccer_updates %>% 
  select(Matchsat:Consat7, Gender:Age)

q5[, c(1:17)] <- sapply(q5[, c(1:17)], as.numeric)

q5_vis <- q5 %>% 
  filter(Consat2 > 0) %>% 
  group_by(Consat2, Matchsat) %>% 
  summarize(count = n()) %>% 
  mutate(toolt = paste0('Food variety satisfaction: ', Consat2,
                        '\nGameday satisfaction: ', Matchsat, 
                        '\nCount: ', count)) %>%
  ggplot(aes(Consat2, Matchsat)) +
  geom_tile_interactive(aes(tooltip = toolt, fill = -count)) + 
  
  theme_classic() + 
  theme(axis.ticks.y = element_blank(), 
        axis.ticks.x = element_blank(), 
        legend.position = "none", 
        axis.text.x = element_blank(), 
        axis.text.y = element_blank()) + 
  
  labs(title = "Satisfaction in food options influence gameday experience",
       x = "Food options satisfaction at the match", 
       y = "Matchday satisfaction")

# view the viz
ggiraph(ggobj = q5_vis)

```

</div>


Key Takeaways
===============================================

+ Robust data set of 684 survey respondents

+ The Reign players being good role models for kids is a strong driver in brand attitude

+ Having a wide range of food options can drive greater gameday experience


Thank You
===============================================
